Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-04-06 sources/bmc_template_submission/bmc_article.tex
fixing italics

%% Biological plausibility of example??
The updated holly tree is based on a single marker, so we expected for it to be
not as well resolved as trees using multiple markers. Nevertheless, all samples
corresponding to the ingroup cluster together in a monophyletic group. We also
note that most samples belonging to the same species also cluster together forming
monophyletic groups. Notable exceptions are Ilex theeizans, which also appears as
non-monophyletic in the original Gottlieb et al. 2005 tree. A visual comparison
of the Yao et al. 2020 tree and the original Gottlieb et al. 2005 tree suggests
that the relationships within the genus Ilex are still being determined, and that
increased taxon sampling is helping with it.

>>>>

%% Biological plausibility of example??
The updated holly tree is based on a single marker, so we expect for it to be
not as well resolved as trees from studies using multiple markers. Although not perfect,
we think the tree seems biologically reasonable in different ways. All samples
corresponding to the ingroup cluster together forming a monophyletic group. We also
note that samples belonging to the same \textit{Ilex} species also cluster together forming
monophyletic groups. A notable exception is \textit{Ilex theeizans}, which appears as
non-monophyletic in the updated tree and the original Gottlieb et al. 2005 tree.
%This suggests that the samples might represent two ifferent species, but further analyses should be conducted
A visual comparison
of the Yao et al. 2020 tree and the original Gottlieb et al. 2005 tree suggests
that the relationships within the genus \textit{Ilex} are still being determined, and that
increased taxon sampling is helping with it.
